A novel distributed nature-inspired algorithm for solving optimization problems

### 2021-10-03 paper.tex
Some corrections here and there

\abstract*{Several bio-inspired algorithms use population evolution as
analogies of nature. In this paper, we present an algorithm inspired by the
biological Life-Cycle of animal species, which consists of several stages:
birth, growth, reproduction, and death. As in nature, we intend to execute all
these stages in parallel and asynchronously on a population that evolves
constantly. From the ground up, we designed the algorithm as a cloud-native
solution using the cloud available resources to divide the processing workload
among several computers or running the algorithm as a cloud service. The
algorithm works concurrently and asynchronously on a constantly evolving
population, using different computers (or containers) independently,
eliminating waiting times between processes. This algorithm seeks to imitate
the natural life cycle, where new individuals are born at any moment and mature
over time, where they age and suffer mutations throughout their lives. In
reproduction, couples match by mutual attraction, where they may have
offspring. Death can happen to everyone: from a newborn to an aged adult, where
the individual's fitness will impact their longevity. As a proof-of-concept, we
implemented the algorithm with Docker containers by solving the OneMax problem
comparing it with a basic (sequential) GA algorithm, where it showed favorable
and promising results.}

@@

One of the problems that we have identified in this research is that most
bio-inspired algorithms are designed with a traditionally sequential
perspective \cite{porto2018evolutionary,back1996evolutionary}, where each
process must wait for the previous task to finish before continuing. Some
architectures address this issue
\cite{valdez2021container,garcia2015evospace,merelo2016nodio}, what
distinguishes us, is that our proposal presents an algorithm designed in its
entirety as a native solution in the cloud, fully distributed, where its
processes are executed in parallel and asynchronously. This technique makes it
easy to scale the computing power according to the complexity required by the
problem \cite{armbrust2010view}.

@@

We present the description of the following sections in our paper. First, we
introduce our algorithm inspired by the Life-Cycle of animal species in
section~\ref{section.proposal}, followed by our experimental configuration and
results in section~\ref{section.experiments}, we analyze and describe some of
our research findings in section~\ref{section.discussion}, and we finalize by
presenting some inferences based on our experiments' results in
section~\ref{section.conclusions}.

@@

This algorithm seeks to imitate the natural life cycle, where new individuals
are born at any moment and mature over time, where they age and suffer
mutations throughout their lives. In reproduction, couples match by mutual
attraction, where they may have offspring. Death can happen to everyone: from a
newborn to an aged adult, where the individual's fitness will impact their
longevity. The general model concept is shown in Figure~\ref{fig.proposal}. The general
flowchart for the Life-Cycle algorithm is described in Figure~\ref{fig.flowchart}.

@@

\begin{figure}
    \includegraphics[width=\textwidth]{img/fig4_flowchart.pdf}
    \caption{Life-Cycle algorithm general flowchart.} \label{fig.flowchart}
    \end{figure}

@@

As in nature, all individuals constantly grow, mature, or age. With increasing
age, individuals may lose strength but also gain more knowledge to solve
problems. We represent this with a possible mutation in each increment of age.
The growth process will take an individual to assess whether it's ready to
mature and undergo changes.

@@

We could have used several strategies to evaluate this attraction. Considering
this algorithm takes a similar focus as the study of bacteria growth in
microbiology, where we can observe and analyze the evolution of a population
over time. As in nature' most species, the bigger a specimen is, the more
attractive it is to its mating candidates. To be consistent with both ideas in
our algorithm, we use the equation of Newton's Law of Universal Gravitation (1)
to calculate the attraction between two individuals, where we visualize the
individual fitness as its mass when using the equation. In previous work,
Newton's Law of Universal Gravitation has shown success in helping to solve
optimization problems \cite{sanchez2014fuzzy,rashedi2009gsa}.

@@

@@

\begin{figure}
    \fbox{\includegraphics[width=\textwidth]{img/fig6_experiment01_chart.pdf}}
    \caption{Box and Whisker chart for the Experiment 1: OneMax DEAP versus Life-Cycle.} \label{fig.experiment1}
    \end{figure}

>>>>

\abstract*{Several bio-inspired algorithms use population evolution as
analogies of Nature. In this paper, we present an algorithm inspired by the
biological Life-Cycle of animal species, which consists of several stages:
birth, growth, reproduction, and death. As in nature, we intend to execute all
% single animals in animal species? Species follow a different lifecycle... - JJ
these stages in parallel and asynchronously on a population that evolves
constantly. From the ground up, we designed the algorithm as a cloud-native
solution leveraging cloud  resources to divide the processing workload
among several computers or running the algorithm as a cloud service. The
algorithm works concurrently and asynchronously on a constantly evolving
population, using different computing nodes (or containers) independently,
eliminating waiting times between processes. This algorithm seeks to imitate
the natural life cycle, where new individuals are born at any moment and mature
over time, where they age and suffer mutations throughout their lives.
% Individuals don't suffer inheritable mutations. That would be a Lamarckian view of evolution - JJ
In
reproduction, couples match by mutual attraction, % But this is related to fitness - JJ
and they may have
offspring. Death can happen to everyone: from a newborn to an aged adult, where
the individual's fitness will impact their longevity. As a proof-of-concept, we
implemented the algorithm with Docker containers by solving the OneMax problem
comparing it with a basic (sequential) GA algorithm, where it showed favorable
and promising results.}

@@

One of the problems that we have identified in this research is that most
bio-inspired algorithms are designed with a traditionally sequential
perspective \cite{porto2018evolutionary,back1996evolutionary}, where each
process must wait for the previous task to finish before continuing. Some
architectures address this issue
\cite{valdez2021container,garcia2015evospace,merelo2016nodio}, what
distinguishes this proposal is the introduction of  an algorithm designed in its
entirety as a native solution in the cloud, fully distributed, where its
processes are executed in parallel and interaction takes place asynchronously. This technique makes it
easy to scale the computing power according to the complexity required by the
problem \cite{armbrust2010view}.

@@

We present the description of the following sections in our paper. First, we
introduce our algorithm inspired by the Life-Cycle of animal species in
% Please use capitalization consistently; I don't think this should go in Caps - JJ
section~\ref{section.proposal}, followed by our experimental configuration and
results in section~\ref{section.experiments}, we analyze and describe some of
our research findings in section~\ref{section.discussion}, and we finalize by
presenting some inferences based on our experiments' results in
section~\ref{section.conclusions}.

@@

This algorithm seeks to imitate the natural life cycle, where new individuals
are born at any moment and mature over time, where they age and suffer
mutations throughout their lives. In reproduction, couples match by mutual
attraction, and they may have offspring. Death can happen to everyone: from a
newborn to an aged adult, where the individual's fitness will impact their
longevity. The general model concept is shown in Figure~\ref{fig.proposal}. The general
flowchart for the Life-Cycle algorithm is described in Figure~\ref{fig.flowchart}.

@@

\begin{figure}
    \includegraphics[width=\textwidth]{img/fig4_flowchart.pdf}
    \caption{Life-Cycle algorithm general flowchart.} \label{fig.flowchart}
% Several terms are introduced here that are not defined in the text, like "champion list" and "attraction" - JJ
    \end{figure}

@@

As in nature, all individuals constantly grow, mature, or age. With increasing
age, individuals may lose strength but also gain more knowledge to solve
problems. We represent this with a possible mutation in each increment of age.
The growth process will take an individual to assess whether it's ready to
mature and undergo changes. % Not learning?  JJ

@@

We could have used several strategies to evaluate this attraction. Considering
this algorithm takes a similar focus as the study of bacteria growth in
microbiology, where we can observe and analyze the evolution of a population
over time. As in nature' most species, the bigger a specimen is, the more
attractive it is to its mating candidates. To be consistent with both ideas in
% Er... not really. It depends on health, mainly - JJ
our algorithm, we use the equation of Newton's Law of Universal Gravitation (1)
to calculate the attraction between two individuals, where we visualize the
individual fitness as its mass when using the equation. In previous work,
Newton's Law of Universal Gravitation has shown success in helping to solve
optimization problems \cite{sanchez2014fuzzy,rashedi2009gsa}.

@@

% to be honest, I find this a bit far fetched. How do you define mass? is it related to fitness? - JJ

@@

\begin{figure}
    \fbox{\includegraphics[width=\textwidth]{img/fig6_experiment01_chart.pdf}}
    \caption{Box and whisker chart for the Experiment 1: OneMax DEAP versus Life-Cycle.} \label{fig.experiment1}
% You need to label axis y - JJ
  \end{figure}
